Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-29 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Floyd example for mechanisms of flooding

Rain is a hazard of tropical storms mostly because it causes flooding. The likelihood and extent of flooding during a tropical storm is related to the amount of rain from the storm, but it is also related to other factors, and storms with similar amounts of rainfall can cause different flooding risks [@Chen2015]. For example, one study of a North Carolina watershed found that streamflow following tropical storms was related not only to rainfall from the storm, but also to top soil saturation and timing of the storm during the hurricane season [@Chen2015]. Therefore, an exposure metric based on rainfall may not perfectly characterize flooding-related risks, and future research could explore either streamflow-based exposure metrics or metrics that combine rain with remote measurements of factors like soil moisture, vegetation states, and meteorological conditions that might modify the amount of flooding caused by a tropical storm's rains [@Chen2015]. The topography of a location (e.g., elevation change in a county) could also affect whether rains from a tropical storm cause a flood, particularly a flash flood [@Czajkowski2011 mentions this, but is not a primary source for this point].

>>>>

Rain is a hazard of tropical storms mostly because it causes flooding. The likelihood and extent of flooding during a tropical storm is related to the amount of rain from the storm, but it is also related to other factors, and storms with similar amounts of rainfall can cause different flooding risks [@Chen2015]. For example, one study of a North Carolina watershed found that streamflow following tropical storms was related not only to rainfall from the storm, but also to top soil saturation and timing of the storm during the hurricane season [@Chen2015]. Therefore, an exposure metric based on rainfall may not perfectly characterize flooding-related risks, and future research could explore either streamflow-based exposure metrics or metrics that combine rain with remote measurements of factors like soil moisture, vegetation states, and meteorological conditions that might modify the amount of flooding caused by a tropical storm's rains [@Chen2015]. The topography of a location (e.g., elevation change in a county) could also affect whether rains from a tropical storm cause a flood, particularly a flash flood [@Czajkowski2011 mentions this, but is not a primary source for this point]. However, @Colle2003 performed an extensive evaluation of Hurricane Floyd (1999) in an effort to understand the mechanisms that led to the development of heavy precipitation and flooding. Though differences in the terrain, namely the Appalachian Mountains, contributed to the development of heavy precipitation in this event, @Colle2003 concluded that flooding would have occured in this region regardless of the presence of the Appalachians and other coastal hills. Instead, the heavy precipitation is thought to have been primarily caused by strong frontogenesis in combination with slant-wise neutrality [@Colle2003]. [Look at Bosart and Dean reference in Colle 2003 reference for more on conditions leading to severe flooding]
